\chapter{Previous Work}

In this section, we'll examine previous work towards answering the LELM Bell basis distinguishability question. We'll first overview the current state of the $d=3$ case, which has been solved for bosons but not for fermions. Then, we'll examine some general bounds. After that, we'll shift focus to the LELM distinguishability question for two hyperentangled particles, which we'll use in Chapter 5.

\section{Work on Equivalent Inputs}

Any answer to the distinguishability question comes in two parts. If one wants to show that $k$ answers the distinguishability question for some particular $d$, they must show both that there exists an LELM device that distinguishes $k$ bell States and that there does not exist a device that distinguishes $k+1$ Bell states. The first part is often much easier, involving the specification of a device and some simple linear algebra to verify the device works.

In ``Methods for Reliable Teleportation,'' there are two pages of algebra used to explain why an LELM device cannot distinguish all four $d=2$ Bell states. In contrast, the proof that there exists an LELM device that does distinguish three Bell states is five sentences \cite{methods}. For the $d=3$ case, explored in Nathaniel Leslie's senior thesis, the discrepancy in work between the existence and non-existence parts of the proof is even more extreme. There are 14 pages (the majority of Chapter 2) devoted to proving that, for bosons, an LELM device cannot distinguish four of the nine $d=3$ Bell states. The proof that an LELM device can distinguish three $d=3$ Bell states is trivial---so trivial, that it's relegated to a footnote in my thesis.\footnote{An LELM device can always distinguish $d$ Bell states. Let the inputs be from different correlation classes, such as $\ket{\Psi_0^0},\ldots,\ket{\Psi_0^{d-1}}$. Let the detection modes be $\ket{0, L}, \ldots, \ket{d-1, L}, \ket{0, R}, \ldots, \ket{d-1, R}$. The detector clicks will reveal the correlation class of the input state, and there is only one input for each correlation class, so our device can reliably distinguish the $d$ inputs!}


\subsection{Nathaniel Leslie's Thesis Work}



\subsection{Other Work}

\section{Work on Hyperentanglement}